COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-15 main.tex
Finish section 3

Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}. In both cases, a Jupiter mass planet is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior. In the first case, Jupiter is given a mildly eccentric (e = 0.05) orbit. In the second case, Jupiter is placed on a circular orbit. We will refer to these simulations as EJ and CJ, respectively.

@@

\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 300 km. This corresponds to a disk containing slightly less than 500,000 planetesimals.

@@

>>>>

Two simulations are run, which are loosely based off of 'Model B' in \citet{2000Icar..143...45R}. In both cases, a Jupiter mass planet is placed on a 5.2 AU orbit around a 1 $M_{\odot}$ star with a disk of planetesimals placed interior. In the first case, Jupiter is placed on a circular orbit. In the second case, Jupiter is placed on a mildly eccentric (e = 0.05) orbit. We will refer to these simulations as CJ and EJ, respectively.

@@

\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ and a diameter of 300 km. This corresponds to a disk containing slightly less than 500,000 planetesimals. Both simulations are evolved for 10,000 years, which is about 800 Jupiter orbits.

@@

For simulation EJ, the effects of secular forcing by Jupiter are applied to the initial conditions. This is done by first assigning Kepler orbital elements to the planetesimals in the same way as simulation CJ and then adding a forced component to the eccentricity vectors $z_{i} = \left( h_{i}, k_{i} \right)$, described by equation \ref{eq:eforced}. For simplicity, a coordinate system is chosen so that $\omega_{g}$ = 0. This allows us to simply add a scalar value to each $h_{i}$, which depends only on the semi-major axis of a planetesimal and Jupiter, along with the eccentricity of Jupiter.

\subsection{Time Stepping Scheme}\label{sec:timestep}

For the purposes of the integrator, there are two relevant timescales in this system. The first is the orbital dynamical time $\sqrt{a^3/G M_{\odot}}$. All particles are placed on a fixed time step of $\Delta T$ = 0.01 yr. This is roughly 3\% of an orbital dynamical time at the inner edge of the planetesimal disk, which is a reasonable time step size for a leapfrog integrator (reference?). The time step for collisions is determined by the planetesimal dynamical timescale ($\sim 1/\sqrt{G \rho}$), which is about 45 minutes. To resolve both of these timescales simultaneously, we use a two-tiered time stepping scheme. At the beginning of each time step, all bodies are placed on the orbital time step. A first pass of collision detection is then run in which the radii of all bodies are inflated by a factor of 2.5. Any bodies with imminent collisions predicted using the inflated radii are placed on a time step that is a factor of 16 smaller than the orbital time step. The purpose of two-tiered scheme is to properly resolve the gravitational interactions between any bodies that will undergo a close encounter. This prevents the coarser base time step from reducing the effectiveness of gravitational focusing, while minimizing the additional computational expense.
